Approximation as Differentiation notes

### 2025-02-22 notes/definitions.tex
Drop general notion of V-enriched category for arbitrary monoidal category for now.

\subsection{Commutative monoids}

A \emph{commutative monoid} $A = (A, \varepsilon, +)$ is a set equipped with distinguished element
$\varepsilon \in A$ called the \emph{unit} and associative binary operation $+$ satisfying $\varepsilon + x =
x$ and $x + \varepsilon = x$ for any $x \in A$. A commutative monoid homomorphism from $A$ to $B$ is any
function $f: A \to B$ which preserves $\varepsilon$ and $+$.

\subsection{Category of commutative monoids}

$\CMon$ is the category whose objects are the commutative monoids $A$ and morphisms $A \to B$ are the
commutative monoid homomorphisms. $\CMon$ is symmetric closed monoidal, with the trivial one-element monoid
$\One$ as terminal object and monoidal product $A \tensor B$ given by the direct product of $A$ and $B$.
$\CMon$ is complete and cocomplete, inheriting all limits and colimits from $\Set$.

@@

A category $C$ is \emph{$\CMon$-enriched} if:
\begin{enumerate}
\item every hom-object $\Hom{C}{A}{B}$ is a commutative monoid with a
\emph{zero} morphism $\zero_{A,B}$ as unit and addition of morphisms $+_{A,B}$ as the monoid operation;
\item composition is a family of morphisms $\Hom{C}{B}{C} \tensor \Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in $\CMon$,
i.e.~satisfies

@@

$\CMon$ is closed monoidal, and so enriched over itself. Every hom-object $\CMon(A,B)$ is a commutative
monoid, with:
\begin{enumerate}
\item unit given by the constant homomorphism that sends every element of $A$ to $\varepsilon_B$;
\item binary operation given pointwise so that $(f + g)(a) = f(a) + f(b)$.
\end{enumerate}

>>>>

\subsection{$\CMon$-enriched categories}

\begin{definition}[Commutative monoid]
A \emph{commutative monoid} $A = (A, \varepsilon, \bullet)$ is a set $A$ equipped with distinguished element
$\varepsilon \in A$ called the \emph{unit} and associative binary operation $\bullet$ satisfying $\varepsilon
\bullet x = x$ and $x \bullet \varepsilon = x$ for any $x \in A$.
\end{definition}

A commutative monoid homomorphism from $A$ to $B$ is any function $f: A \to B$ which preserves $\varepsilon$
and $\bullet$.

\begin{definition}[Category of commutative monoids]
Define $\CMon$ to be the category whose objects are the commutative monoids $A$ and morphisms $A \to B$ are
the commutative monoid homomorphisms.
\end{definition}

$\CMon$ is symmetric closed monoidal, with the trivial one-element monoid $\One$ as terminal object and
monoidal product $A \tensor B$ given by the direct product of $A$ and $B$. $\CMon$ is complete and cocomplete,
inheriting all limits and colimits from $\Set$.

@@

We note that if a category $C$ is \emph{$\CMon$-enriched}, then:
\begin{enumerate}
\item every hom-object $\Hom{C}{A}{B}$ is a commutative monoid (writing $\zero_{A,B}$ for the unit and
$+_{A,B}$ for the binary operation);
\item composition is given by a family of morphisms $\Hom{C}{B}{C} \tensor \Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in
$\CMon$, i.e.~satisfies

@@

$\CMon$ is closed monoidal, and so enriched over itself. Every hom-object $\CMon(A,B)$ is a commutative
monoid, with:
\begin{enumerate}
\item unit given by the constant homomorphism sending every element of $A$ to $\varepsilon_B$;
\item binary operation given pointwise so that $(f + g)(a) = f(a) + f(b)$.
\end{enumerate}
